Adolescent well-being in the digital age

### 2022-03-24 00-clean.Rmd
Drop missing sex rows
Fix missing SEs

# There is one 13 year old which resulted in a NA and we drop it
gwp <- drop_na(gwp, age)
```

@@

```{r gallup-summarise}
gwp <- gwp %>%
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  group_by(country, year, sex, age, outcome) %>%
  summarise(
    n = n(),
    se = sd(val, na.rm = TRUE) / sqrt(n),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()
```

>>>>

# There is one 13 year old which resulted in a NA and we drop it
gwp <- drop_na(gwp, age)

# Some sex values are missing, drop those
gwp <- drop_na(gwp, sex)
```

@@

```{r gallup-summarise}
gwp <- gwp %>%
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  group_by(country, year, sex, age, outcome) %>%
  summarise(
    n = n(),
    se = sd(val, na.rm = TRUE) / sqrt(n),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()

# Note that if there is no response variance, SE will be zero, and if there is only 1 response, SE will be NA. Here we fix those by assigning them the maximum SE (0.5)
gwp <- gwp %>% 
  mutate(
    se = if_else(is.na(se) | se == 0, 0.5, se)
  )
```
